The Strucplot Framework---Visualizing Multi-way Contingency Tables

### 2005-09-26 trunk/vcd/inst/doc/strucplot.Rnw
bug fixes: legend scales like plot now, and strucplot works with utf8 characters.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@462 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}[h]
\begin{center}
<<vcdlayout,fig=TRUE,echo=FALSE,width=6,height=5>>=
    pushViewport(vcd:::vcdViewport(legend = T, mar =4))
    seekViewport("plot")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("plot", gp = gpar(fontsize = 30))
    seekViewport("legend")
    grid.text("legend", rot = 90, gp = gpar(fontsize = 30))
    grid.rect(gp = gpar(lwd = 3))
    seekViewport("pval")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("pval", gp = gpar(fontsize = 30))
    seekViewport("margin_top")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_top", gp = gpar(fontsize = 30))
    seekViewport("margin_bottom")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_bottom", gp = gpar(fontsize = 30))
    seekViewport("margin_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_right", rot = 90, gp = gpar(fontsize = 30))
    seekViewport("margin_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_left", rot = 90, gp = gpar(fontsize = 30))
    seekViewport("corner_top_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[A]", gp = gpar(fontsize = 30))
    seekViewport("corner_top_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[B]", gp = gpar(fontsize = 30))
    seekViewport("corner_bottom_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[C]", gp = gpar(fontsize = 30))
    seekViewport("corner_bottom_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[D]", gp = gpar(fontsize = 30))
@ 
\caption{Viewport layout for strucplot displays with their names. [A] =
  ``corner\_top\_left'', [B] = ``corner\_top\_right'', 
  [C] = ``corner\_bottom\_left'', [D] = ``corner\_bottom\_right''.}
\label{fig:layout}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=0.6\textwidth}
\begin{figure}[h]
\begin{center}
<<vcdlayout,fig=TRUE,echo=FALSE,width=6,height=6>>=
    pushViewport(vcd:::vcdViewport(legend = T, mar =4))
    seekViewport("plot")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("plot", gp = gpar(fontsize = 30))
    seekViewport("legend")
    grid.text("legend", rot = 90, gp = gpar(fontsize = 30))
    grid.rect(gp = gpar(lwd = 3))
    seekViewport("pval")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("pval", gp = gpar(fontsize = 30))
    seekViewport("margin_top")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_top", gp = gpar(fontsize = 30))
    seekViewport("margin_bottom")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_bottom", gp = gpar(fontsize = 30))
    seekViewport("margin_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_right", rot = 90, gp = gpar(fontsize = 30))
    seekViewport("margin_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("margin_left", rot = 90, gp = gpar(fontsize = 30))
    seekViewport("corner_top_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[A]", gp = gpar(fontsize = 30))
    seekViewport("corner_top_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[B]", gp = gpar(fontsize = 30))
    seekViewport("corner_bottom_left")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[C]", gp = gpar(fontsize = 30))
    seekViewport("corner_bottom_right")
    grid.rect(gp = gpar(lwd = 3))
    grid.text("[D]", gp = gpar(fontsize = 30))
@ 
\caption{Viewport layout for strucplot displays with their names. [A] =
  ``corner\_top\_left'', [B] = ``corner\_top\_right'', 
  [C] = ``corner\_bottom\_left'', [D] = ``corner\_bottom\_right''.}
\label{fig:layout}
\end{center}
\end{figure}
\setkeys{Gin}{width=0.7\textwidth}
